Newly Left-Behind Children's Educational Performance Drops Slightly After Parents Migrated

### 2022-06-23 MScThesisText.tex
First draft

  pdftitle={Parental Migration and Left-Behind Children's Cognitive and Academic Performances},

@@

\title{Parental Migration and Left-Behind Children's Cognitive and Academic Performances}
\author{Jiancheng Gu\textsuperscript{1}}
\date{}

@@

Millions of children are resided in their home communities but separated from their parents as either one or both parents have migrated for work (Antia et al., 2020). These are the so-called ``left behind children.'' They are common in migrant-sending regions, such as Latin America, Sub-Sahara Africa, East Europe, and large parts of Asia. Researchers estimated that one-sixth of Mexican children (DeWaard et al., 2018), one-fifth of Bulgarian children, (Popova, 2018), and one-fourth of Chinese children were living apart from their migrating parents (NBS et al., 2017).

How are children faring when parents have migrated? Scholars have obtained mixed results due to the differential effects of parental migration. Consider children's education. (Van Hook \& Glick, 2020) labor migrants send remittances back home, which can fund children's schooling as well as improve their nutritional and living conditions. The inflow of remittances, however, cannot substitute for the loss of parental care. Parental migration decreases the amount and quality of parental guidance, protection, and support. It is uncertain how these two opposing effects together shape children's educational performance, which merits empirical investigation.

@@

To what extent do parental migration affect the cognitive development and academic performance of left-behind children in the short term? I analyze the data from a nationally representative two-wave panel survey. The sample includes children in both urban and rural areas. I develop a difference-in-differences design for causal inference. The dependent variables include children's cognitive test score and Chinese, mathematics, and English exam scores.

@@

Between parental migration and children's education, the mechanisms trace to two theoretical frameworks. One model, the resource generation model, holds that parental migration brings forth greater resources in the form of economic capital. Economic capital is, in Bourdieu's words, ``immediately and directly convertible into money and may be institutionalized in the form of property rights'' (2002, p. 16). Economic capital is transferable to human capital, which is the stock of ``skills, talents, health, and expertise'' in people that enhance their productivity (Botev et al., 2019; Goldin, 2016). (D. Yang, 2008) noted that a depreciation of Filipino peso increased the amount of foreign remittances, which subsequently boosted children's school enrollment and educational expenditure. In China, (Chang et al., 2019) interviewed migrant workers and their family members. Oftentimes, they found that labor migration presented the only way to sustain their children's education and livelihood.

@@

Researchers obtained mixed results regarding how parental migration affects children's education. (Botezat \& Pfeiffer, 2020) studied the case of Romania and found a positive effect of parents' migration on academic grades of adolesents aged eleven to fifteen. (Wang et al., 2019) collected data from junior high school students in central China and found no effect of parental on left-behind children's achievement in mathematical test. Studying four Chinese provinces, (Brauw \& Giles, 2017) showed that as ample migration opportunities appeared in villages, enrollment to senior high school decreased. (Nguyen, 2016) demonstrated that parental migration was associated with lower cognitive capabilities among Indian and Vietnamese children aged five to eight. The inconsistency can result from factors such as the left-behind children's age and gender, the migrant parent's original domicile and eventual destination, and the arrangement of which parent migrate for how long.

@@

The social norms designate men as breadwinners and women as caregivers. Studies noted that in some Asian and Latin American societies, children are more likely to accept fathers' migration than mothers' (Murphy, 2022). Left behind children may even resent their migrant mothers, viewing them as transgressing on the expected care-giving roles. I propose the second hypothesis:

@@

Three features make China a suitable case for studying left behind children. The first feature is the huge scale of internal labor migration. According to the National Bureau of Statistics, the year 2021 recorded 292.5 million in-country migrant workers (NBS, 2022). The number of left behind Chinese children reached 68.7 million in 2015 (NBS et al., 2017). The second feature is the neoliberal welfare regime. Neoliberalism extends the logic of the market to most spheres of human life. Driven by the neoliberal doctrine, the government shifts its responsibilities of social services and welfare to individuals and communities. Since China initiated pro-market reforms in the 1980s, the state has reduced its welfare provisions and passed them to individuals and families (Zhan, 2020). The third feature is the authoritarian control against citizens. According to Gu (2021), the hukou (household registration) system controls people's mobility by binding a household's public welfare access with its place of registry. One can move to another place freely but cannot change hukou freely. For a rural household member moving to the city, it takes much time and effort to apply for urban hukou status. Without an urban hukou they cannot send children to public school in the host city. Facing financial and policy constraints, many migrant laborers have to leave children in their original domiciles.

The research on China's left behind children has three major shortcomings. First, most literature focuses on children left behind in rural areas while neglecting the urban counterparts. (NBS et al., 2017) stated that the number of urban left behind children had been growing and expected that the trend would continue. The second shortcoming lies in data and sampling. Some studies draw from cross-sectional data, making it hard to infer causal relations (Jin et al., 2020; Zhou et al., 2014). Others suffer from a limited sample size of less than one thousand participants or a limited geographic coverage of one or a few towns (Jin et al., 2020; Liu et al., 2021; Shu, 2021; F. Yang et al., 2022). The third shortcoming lies in the selection and measurement of outcome. (Chang et al., 2019; Wang et al., 2019) measured students' educational performance with the test score of only one academic subject, namely mathematics. The test results of multiple subjects should be included to measure comprehensive academic achievement.

@@

I explored two categories of adolescence development: cognitive and academic abilities. One key dependent variable, the student's cognitive skill, was measured by a fifteen-minute standardized test. The test covered three types of reasoning: verbal, visuospatial, and numerical. The CEPS research team calculated the raw score based on the Item Response Theory and then standardized the score with a mean of zero and standard deviation of one.

Another dependent variables concerned students' academic performance. This was measured by the total scores of mid-term exams in Chinese, mathematics, and English as provided by each school. These three subjects constitute the core parts in the senior high school entrance exam. Within one particular school, teachers of the same subject use the same syllabus, administering the same exams during a given assessment period. Therefore, test scores for core subjects are reliable indicators of learning performance in the same school and cohort. I aligned different grading scales (full mark of 100, 120, and 150 for one subject) to the hundred-point scale. Accordingly, the total score of three subjects has a 300-point scale.

@@

I adopted R (Version 4.2.0; R Core Team, 2022) and the R-packages \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), and \emph{tinylabels} (Version 0.2.3; Barth, 2022) for all the analyses, the \texttt{fixest} package for building the econometric models (Bergé, 2018), and the \texttt{modelsummary} package for presenting the results (Arel-Bundock, 2022). I built a two-way fixed effect model in a difference-in-differences (DID) design, following Bai and colleagues' (2018; 2020) approach. The model served to analyze the educational outcome of children newly left behind by parents vis-a-vis that of children staying together with parents. I first specified an unrestricted and unadjusted model: \[\Delta score_{i,j} = \alpha + \beta \cdot migr_{i} + \gamma \cdot C_{1} + \lambda \cdot C_{2} + \theta \cdot score_{i,j;1} + \varepsilon_{i,j}\] For student \(i\) taking the test of type \(j\), \(\Delta score_{i,j}\) is the change in test score between baseline and follow-up surveys, \(migr_{i}\) is the treatment dummy variable, \(C_{1}\) and \(C_{2}\) are respectively the classroom fixed-effects at baseline and follow-up, and \(score_{i,j;1}\) is the test score at baseline. The model is unrestricted because it does not restrict on the coefficient associated with the baseline scores. The model is unadjusted as it does not adjust for additional covariates. Theoretically, it is unnecessary to include covariates that vary over group but remain constant over time; They would cancel out in the two-way fixed effect model (Huntington-Klein, n.d.). The standard errors were clustered at the classroom level.

In addition, I present an unrestricted and adjusted DID model: \[\Delta score_{i,j} = \alpha + \beta \cdot migr_{i} + \gamma \cdot C_{1} + \lambda \cdot C_{2} + \theta \cdot score_{i,j;1} + \zeta \cdot X_{i} + \varepsilon_{i,j}\] where \(X_{i}\) is the vector of covariates capturing the characteristics of children, their parents, and their households. The control variables were measured in the baseline survey. This version of model lifts the restriction that covariates from the baseline survey would be associated with a coefficient that equals one.

@@

The table below provides the summary statistics.

\begin{longtable}[]{@{}lrrrr@{}}
\caption{The independent variables}\tabularnewline
\toprule
& Mean & SD & Min & Max \\
\midrule
\endfirsthead
\toprule
& Mean & SD & Min & Max \\
\midrule
\endhead
migr & 0.16 & 0.36 & 0.00 & 1.00 \\
Cognitive score difference & 0.27 & 0.80 & -2.88 & 4.03 \\
Cognitive score at wave 1 & 0.15 & 0.85 & -2.03 & 2.33 \\
Cognitive score at wave 2 & 0.42 & 0.78 & -3.14 & 2.06 \\
Academic exam score difference & -8.82 & 33.21 & -207.50 & 166.00 \\
Academic exam score at wave 1 & 213.11 & 49.46 & 19.33 & 297.50 \\
Academic exam score at wave 2 & 204.29 & 55.41 & 0.00 & 293.33 \\
\bottomrule
\end{longtable}

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2661}}
  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1743}}
  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1835}}
  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1835}}
  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1927}}@{}}
\caption{Parental migration's effect on children's cognitive abilities}\tabularnewline
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Any Parent Absent
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Only Mother Absent
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Only Father Absent
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Both Parents Absent
\end{minipage} \\
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Any Parent Absent
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Only Mother Absent
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Only Father Absent
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Both Parents Absent
\end{minipage} \\
\midrule
\endhead
Explanator & -0.09** & -0.04 & -0.14*** & -0.08 \\
& (0.03) & (0.05) & (0.04) & (0.06) \\
W1 score & -0.67*** & -0.67*** & -0.67*** & -0.67*** \\
& (0.02) & (0.02) & (0.02) & (0.02) \\
child.age & -0.07*** & -0.06** & -0.07*** & -0.08*** \\
& (0.02) & (0.02) & (0.02) & (0.02) \\
child.is.girl & -0.01 & 0.00 & 0.00 & -0.01 \\
& (0.02) & (0.02) & (0.02) & (0.02) \\
child.health.self.rated & -0.02 & -0.02 & -0.02 & -0.02 \\
& (0.01) & (0.01) & (0.01) & (0.01) \\
child.has.rural.hukou & -0.01 & 0.00 & -0.01 & 0.00 \\
& (0.02) & (0.03) & (0.03) & (0.03) \\
child.number.of.sibling & -0.03 & -0.02 & -0.02 & -0.02 \\
& (0.02) & (0.02) & (0.02) & (0.02) \\
child.went.to.preschool & 0.07* & 0.06† & 0.05† & 0.07* \\
& (0.03) & (0.03) & (0.03) & (0.03) \\
child.had.skipped.grade & -0.17 & -0.11 & -0.20 & -0.10 \\
& (0.12) & (0.12) & (0.12) & (0.12) \\
child.had.repeated.grade & -0.08* & -0.11** & -0.07† & -0.06 \\
& (0.04) & (0.04) & (0.04) & (0.04) \\
child.in.boarding.school & 0.04 & 0.02 & 0.02 & 0.01 \\
& (0.04) & (0.04) & (0.04) & (0.04) \\
child.educational.aspiration & 0.07*** & 0.07*** & 0.07*** & 0.08*** \\
& (0.01) & (0.01) & (0.01) & (0.01) \\
child.is.ethnic.minority & 0.04 & 0.04 & 0.02 & 0.02 \\
& (0.06) & (0.06) & (0.06) & (0.06) \\
parent.expectation.on.child & 0.08*** & 0.09*** & 0.09*** & 0.09*** \\
& (0.02) & (0.02) & (0.02) & (0.02) \\
parent.has.white.collar.job & 0.01 & -0.01 & 0.01 & 0.00 \\
& (0.03) & (0.03) & (0.03) & (0.03) \\
parent.educational.level & 0.01 & 0.01 & 0.01 & 0.01 \\
& (0.01) & (0.01) & (0.01) & (0.01) \\
home.economic.resource & -0.02 & -0.01 & 0.00 & 0.00 \\
& (0.02) & (0.02) & (0.02) & (0.02) \\
home.extracurricular.book & 0.01 & 0.00 & 0.01 & 0.00 \\
& (0.01) & (0.01) & (0.01) & (0.01) \\
home.has.internet & -0.01 & -0.01 & -0.02 & -0.02 \\
& (0.03) & (0.03) & (0.03) & (0.03) \\
Num.Obs. & 4088 & 3706 & 3703 & 3583 \\
R2 & 0.525 & 0.533 & 0.537 & 0.530 \\
R2 Adj. & 0.458 & 0.459 & 0.464 & 0.452 \\
R2 Within & 0.409 & 0.416 & 0.418 & 0.413 \\
FE: clsids & X & X & X & X \\
FE: w2clsids & X & X & X & X \\
\bottomrule
\end{longtable}

@@

Researchers noted that migrants represent a positively selected group compared to non-migrants (Van Hook \& Glick, 2020). One technique to tackle the selectivity issue is matching. This method works by pairing a unit in the treatment group with one or several units in the control group based on observable covariates. Popular choices include coarsened exact matching (CEM) (Waldman, 2022), nearest-neighbor propensity score matching (PSM) (H. Xu \& Xie, 2015), and nearest-neighbor Mahalanobis distance matching (MDM) (Guo et al., 2021). CEM is superior in achieving balance as it optimizes the entire joint distribution of covariates. The downside is that it leaves many units without an exact match and discards these unmatched units. The nearest-neighbor matching examines all the treated units and selects the closest eligible control unit to be paired. The eligibility as the ``closest'' can be determined with the differences in Mahalanobis distance or in propensity score. Propensity score denotes the probability of receiving treatment based on the specified covariates. Nearest-neighbor PSM does not try to optimize any condition as each pairing ignores how other units will be or have been paired. This matching method may result in more ``imbalance, model dependence, and bias'' on highly balanced data (King \& Nielsen, 2019).

I conducted matching with all the covariates used in the adjusted DID model. I first attempted CEM, which left most units unmatched and resulted in a tiny sample. Then I combined exact matching (based on the student's county of residence) and nearest neighbor PSM (based on the other covariates), which is the configuration of Bai and others (2018). Exact matching based on county of residence preserves the original geographic distribution. The propensity score was estimated using a logistic regression of the treatment on the covariates. The matching ratio was set at one treatment unit with up to three control units.

Alike are the results with matching and those without. In the models of cognitive abilities, I obtained negative, statistically significant coefficients on the treatment variables in the any parent migrated household and only father migrated households. In the models of academic abilities, the treatment variables' coefficients are negative and statistically significant in the any parent migrated households and only mother migrated households. The magnitudes of the coefficients are also similar.

>>>>

  pdftitle={Newly Left-Behind Children's Educational Performance Drops Slightly After Parents Migrated},

@@

\title{Newly Left-Behind Children's Educational Performance Drops Slightly After Parents Migrated}
\author{Jiancheng Gu\textsuperscript{1}}
\date{}

@@

Millions of children are resided in their home communities but separated from their parents as either one or both parents have migrated for work (Antia et al., 2020). These are the so-called ``left-behind children'' or ``stay-behind children.'' They are common in migrant-sending regions, such as Latin America, Sub-Sahara Africa, East Europe, and large parts of Asia. Researchers estimated that one-sixth of Mexican children (DeWaard et al., 2018), one-fifth of Bulgarian children, (Popova, 2018), and one-fourth of Chinese children were living apart from their migrating parents (NBS et al., 2017).

How are stay-behind children faring when parents have migrated? Scholars have obtained mixed results due to the differential effects of parental migration. Consider children's education. According to the review articles by De Brauw (2019) and by Van Hook and Glick (2020), labor migrants send remittances back home, which can fund children's schooling as well as improve their nutritional and living conditions. The inflow of remittances, however, cannot substitute for the loss of parental care. Parental migration decreases the amount and quality of parental guidance, protection, and support. It is uncertain how these two opposing effects together shape children's educational performance, which merits empirical investigation.

@@

In this thesis, my research question is: To what extent do parental migration affect the educational performance of left-behind children in the short term? I choose China as the case and analyze data from a two-wave panel survey. The nationally representative sample includes children in both urban and rural areas. I develop a difference-in-differences model for causal inference and apply propensity score matching for robustness check. The outcome was measured with children's cognitive test score and academic exam scores. I demonstrate that parental migration reduces the educational performance of children staying behind, but only to a small extent.

@@

Between parental migration and children's education, the mechanisms trace to two theoretical frameworks. One is the resource generation model. It holds that parental migration brings forth greater resources in the form of economic capital. Economic capital is, in Bourdieu's words, ``immediately and directly convertible into money and may be institutionalized in the form of property rights'' (2002, p. 16). Economic capital is transferable to human capital, which is the stock of ``skills, talents, health, and expertise'' in people that enhance their productivity (Botev et al., 2019; Goldin, 2016). (D. Yang, 2008) noted that in the Philippes, a sharp depreciation of peso increased the amount of remittances from migrant laborers working abroad. This subsequently boosted children's school enrollment and educational expenditure. In China, (Chang et al., 2019) interviewed migrant workers and their family members. Oftentimes, they found that labor migration presented the only way to sustain their children's education and livelihood.

@@

Researchers obtained mixed results regarding how parental migration affects children's education. Botezat and Pfeiffer (2020) studied the case of Romania and found a positive effect of parents' migration on academic grades of adolescents aged eleven to fifteen. Wang and others (2019) collected data from junior high school students in central China and found no effect of parental on left-behind children's achievement in mathematical test. Studying four Chinese provinces, De Brauw and Giles (2017) showed that as ample migration opportunities appeared in villages, enrollment to senior high school decreased. Nguyen (2016) demonstrated that parental migration was associated with lower cognitive capabilities among Indian and Vietnamese children aged five to eight. The inconsistency can result from factors such as the left-behind children's age and gender, the migrant parent's original domicile and eventual destination, and the arrangement of which parent migrate for how long.

@@

In China, the social norms designate men as breadwinners and women as caregivers. Studies noted that in some Asian and Latin American societies, children are more likely to accept fathers' migration than mothers' (Murphy, 2022). Left behind children may even resent their migrant mothers, viewing them as transgressing on the expected care-giving roles. I propose the second hypothesis:

@@

Three features make China a suitable case for studying left behind children. The first feature is the huge scale of internal labor migration. According to the National Bureau of Statistics, the year 2021 recorded 292.5 million in-country migrant workers (NBS, 2022). They form the backbone of essential industries, such as delivery, transportation, and manufacturing. The number of left behind Chinese children reached 68.7 million in 2015 (NBS et al., 2017). The second feature is the neoliberal welfare regime. Neoliberalism extends the logic of the market to most spheres of human life. Driven by the neoliberal doctrine, the government shifts its responsibilities of social services and welfare to individuals and communities. Since China initiated pro-market reforms in the 1980s, the state has reduced its welfare provisions and passed them to individuals and families (Duckett, 2020). The third is the authoritarian control against citizens. According to Gu (2021) and Zhang (2018), the hukou (household registration) system controls people's mobility by binding a household's public welfare access with its place of registry. One can move out of town freely but cannot change hukou freely. For rural household members moving to the city, it takes months -- if not years -- to apply for a new hukou. Before receiveing urban hukou, they enjoy limited access to public service in the host city, including public education for children. Facing financial and policy constraints, many migrant laborers have to leave children in their hometowns (Gu, 2021; Zhang, 2018). Migrant laborers had attempted to strike or protest, only to meet with police crackdown (Chan \& Selden, 2017).

The existing research about China's left behind children has three major shortcomings that I aim to tackle. The first is that most literature focuses on children left behind in rural areas while neglecting the urban counterparts. I included urban left behind children as well. The National Bureau of Statistics stated that the number of urban left behind children had been growing and expected that the trend would continue (NBS et al., 2017). The second shortcoming lies in data and sampling. Some studies draw from cross-sectional data, making it hard to infer causal relations (Jin et al., 2020; Zhou et al., 2014). Others suffer from a limited sample size of less than one thousand participants or a limited geographic coverage of one or a few towns (Jin et al., 2020; Y. Liu et al., 2021; Shu, 2021; F. Yang et al., 2022). I adopted a nationally representative two-wave panel dataset. The third shortcoming lies in the measurement of outcome. (Chang et al., 2019; Wang et al., 2019) measured students' educational performance with the test score of only one academic subject, namely mathematics. I included the test results of multiple subjects to measure comprehensive academic achievement.

@@

I explored two categories of educational performance: cognitive and academic abilities. One key dependent variable, the student's cognitive skill, was measured by a fifteen-minute standardized test. The test covered three types of reasoning: verbal, visuospatial, and numerical. The CEPS research team calculated the raw score based on the Item Response Theory and then standardized the score with a mean of zero and standard deviation of one.

Another dependent variables concerned students' academic performance. This was measured by the total scores of mid-term exams in Chinese, mathematics, and English as provided by each school. These three subjects constitute the core parts in the senior high school entrance exam. Junior high school students study these subjects throughout three academic years. Within each cohort in one particular school, teachers adopt the same syllabus and administer the same exams during a given assessment period. Therefore, test scores for core subjects are reliable indicators of learning performance in the same school and cohort. I aligned different grading scales (full mark of 100, 120, and 150 for one subject) to the hundred-point scale. After the conversion, I checked for abnormal values outside the 0-100 range. 31 observations are outliers, accounting for less than one percent of the sample. I trim the values of subject exam score with minimum of zero and maximum of one hundred. In this way, I can limit the impact of outliers while retaining these observations in the sample. After trimming, I aggregated the subject exam scores to obtain a total score of a 300-point scale.

@@

I adopted \texttt{R} for all the analyses, the \texttt{fixest} package for building the econometric models (Berge et al., 2022), and the \texttt{modelsummary} package for presenting the results (Arel-Bundock, 2022). I built a two-way fixed effect model in a difference-in-differences (DID) design, following Bai and colleagues' (2018; 2020) approach. The model served to analyze the educational outcome of children newly left behind by parents vis-a-vis that of children staying together with parents. I first specified an unrestricted and unadjusted model: \[\Delta score_{i,j,k} = \alpha + \beta \cdot migr_{i} + \gamma \cdot C_{i} + \lambda \cdot C_{j} + \theta \cdot score_{i,j;1} + \varepsilon_{i,j,k}\] For student \(i\) in class \(j\) in baseline and class \(k\) in endline, \(\Delta score_{i,j}\) is the change in test score between baseline and follow-up surveys, \(migr_{i}\) is the treatment dummy variable, \(C_{j}\) and \(C_{k}\) are respectively the classroom fixed-effects at baseline and follow-up, and \(score_{i,j,k;1}\) is the test score at baseline. The model is unrestricted because it does not restrict on the coefficient associated with the baseline scores. The model is unadjusted as it does not adjust for additional covariates. Theoretically, it is unnecessary to include covariates that vary over group but remain constant over time; They would cancel out in the two-way fixed effect model (Huntington-Klein, n.d.). The standard errors were clustered at the classroom level.

In addition, I present an unrestricted and adjusted DID model: \[\Delta score_{i,j,k} = \alpha + \beta \cdot migr_{i} + \gamma \cdot C_{i} + \lambda \cdot C_{j} + \theta \cdot score_{i,j,k;1} + \zeta \cdot X_{i} + \varepsilon_{i,j,k}\] where \(X_{i}\) is the vector of covariates capturing the characteristics of children, their parents, and their households. The control variables were measured in the baseline survey. This version of model lifts the restriction that covariates from the baseline survey would be associated with a coefficient that equals one.

@@

The tables below provide the whole-sample summary statistics. In addition, the violin plots in the appendix visualize the distribution of outcome variables for the treatmeng group and the control group.

\begin{longtable}[]{@{}lrrrr@{}}
\caption{The independent variables}\tabularnewline
\toprule
& Mean & SD & Min & Max \\
\midrule
\endfirsthead
\toprule
& Mean & SD & Min & Max \\
\midrule
\endhead
Cognitive score difference & 0.27 & 0.80 & -2.88 & 4.03 \\
Cognitive score at wave 1 & 0.15 & 0.85 & -2.03 & 2.33 \\
Cognitive score at wave 2 & 0.42 & 0.78 & -3.14 & 2.06 \\
Academic exam score difference & -8.82 & 33.21 & -207.50 & 166.00 \\
Academic exam score at wave 1 & 213.11 & 49.46 & 19.33 & 297.50 \\
Academic exam score at wave 2 & 204.29 & 55.41 & 0.00 & 293.33 \\
\bottomrule
\end{longtable}

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2661}}
  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1743}}
  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1835}}
  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1835}}
  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1927}}@{}}
\caption{Parental migration's effect on children's academic abilities}\tabularnewline
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Any Parent Absent
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Only Mother Absent
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Only Father Absent
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Both Parents Absent
\end{minipage} \\
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Any Parent Absent
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Only Mother Absent
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Only Father Absent
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Both Parents Absent
\end{minipage} \\
\midrule
\endhead
Explanator & -0.09** & -0.04 & -0.14*** & -0.08 \\
& (0.03) & (0.05) & (0.04) & (0.06) \\
W1 score & -0.67*** & -0.67*** & -0.67*** & -0.67*** \\
& (0.02) & (0.02) & (0.02) & (0.02) \\
child.age & -0.07*** & -0.06** & -0.07*** & -0.08*** \\
& (0.02) & (0.02) & (0.02) & (0.02) \\
child.is.girl & -0.01 & 0.00 & 0.00 & -0.01 \\
& (0.02) & (0.02) & (0.02) & (0.02) \\
child.health.self.rated & -0.02 & -0.02 & -0.02 & -0.02 \\
& (0.01) & (0.01) & (0.01) & (0.01) \\
child.has.rural.hukou & -0.01 & 0.00 & -0.01 & 0.00 \\
& (0.02) & (0.03) & (0.03) & (0.03) \\
child.number.of.sibling & -0.03 & -0.02 & -0.02 & -0.02 \\
& (0.02) & (0.02) & (0.02) & (0.02) \\
child.went.to.preschool & 0.07* & 0.06† & 0.05† & 0.07* \\
& (0.03) & (0.03) & (0.03) & (0.03) \\
child.had.skipped.grade & -0.17 & -0.11 & -0.20 & -0.10 \\
& (0.12) & (0.12) & (0.12) & (0.12) \\
child.had.repeated.grade & -0.08* & -0.11** & -0.07† & -0.06 \\
& (0.04) & (0.04) & (0.04) & (0.04) \\
child.in.boarding.school & 0.04 & 0.02 & 0.02 & 0.01 \\
& (0.04) & (0.04) & (0.04) & (0.04) \\
child.educational.aspiration & 0.07*** & 0.07*** & 0.07*** & 0.08*** \\
& (0.01) & (0.01) & (0.01) & (0.01) \\
child.is.ethnic.minority & 0.04 & 0.04 & 0.02 & 0.02 \\
& (0.06) & (0.06) & (0.06) & (0.06) \\
parent.expectation.on.child & 0.08*** & 0.09*** & 0.09*** & 0.09*** \\
& (0.02) & (0.02) & (0.02) & (0.02) \\
parent.has.white.collar.job & 0.01 & -0.01 & 0.01 & 0.00 \\
& (0.03) & (0.03) & (0.03) & (0.03) \\
parent.educational.level & 0.01 & 0.01 & 0.01 & 0.01 \\
& (0.01) & (0.01) & (0.01) & (0.01) \\
home.economic.resource & -0.02 & -0.01 & 0.00 & 0.00 \\
& (0.02) & (0.02) & (0.02) & (0.02) \\
home.extracurricular.book & 0.01 & 0.00 & 0.01 & 0.00 \\
& (0.01) & (0.01) & (0.01) & (0.01) \\
home.has.internet & -0.01 & -0.01 & -0.02 & -0.02 \\
& (0.03) & (0.03) & (0.03) & (0.03) \\
Num.Obs. & 4088 & 3706 & 3703 & 3583 \\
R2 & 0.525 & 0.533 & 0.537 & 0.530 \\
R2 Adj. & 0.458 & 0.459 & 0.464 & 0.452 \\
R2 Within & 0.409 & 0.416 & 0.418 & 0.413 \\
FE: clsids & X & X & X & X \\
FE: w2clsids & X & X & X & X \\
\bottomrule
\end{longtable}

@@

Researchers noted that migrants represent a positively selected group compared to non-migrants (Van Hook \& Glick, 2020), which may present systematic differences between left behind children and their non-left-behind peers. One technique to tackle this selection bias is matching. This method works by pairing a unit in the treatment group with one or several units in the control group based on observable covariates. Popular choices include coarsened exact matching (CEM) (Waldman, 2022) and nearest-neighbor propensity score matching (PSM) (H. Xu \& Xie, 2015). As Greifer (2022) introduced, CEM is superior in achieving balance as it optimizes the entire joint distribution of covariates. The downside is that it leaves many units without an exact match and discards these unmatched units. The nearest-neighbor matching examines all the treated units and selects the closest control unit to be paired. The eligibility as the ``closest'' can be determined with the differences in propensity score. Propensity score denotes the probability of receiving treatment based on the specified covariates. Nearest-neighbor PSM does not try to optimize any condition; each pairing ignores how other pairing will or have occurred (Greifer, 2022). King and Nelson (2019) argue against this matching method as it risks more ``imbalance, model dependence, and bias'' for highly balanced data.

I adopted the \texttt{MatchIt} package to perform matching with all the covariates of the adjusted DID model (Ho et al., 2022). I first attempted CEM, which left most units unmatched and resulted in a tiny sample. Then I combined exact matching (based on the student's county of residence) and nearest neighbor PSM (based on the other covariates), which is the configuration of Bai and others (2018). Exact matching based on county of residence preserves the original geographic distribution. The propensity score was estimated using a logistic regression of the treatment on the covariates. The matching ratio was set at one treatment unit with up to three control units. The matching produced absolute standardized mean differences below 0.1 for all but a few covariates.

Alike are the results from DID models with matching (DIDM) and those without. In the models of cognitive abilities, I obtained negative, statistically significant coefficients on the treatment variables in the any parent migrated household and only father migrated households. In the models of academic abilities, the treatment variables' coefficients are negative and statistically significant for the any parent migrated households and only mother migrated households. The significance level of any parent migration drops to ten percent. In all models, the magnitudes of the statistically significant coefficients are similar. I present the unadjusted DIDM models below and the adjusted DIDM models in the appendix.

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1398}}
  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2043}}
  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2151}}
  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2151}}
  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2258}}@{}}
\caption{Parental migration's effect on children's cognitive abilities, estimated with matching}\tabularnewline
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Any Parent Absent
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Only Mother Absent
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Only Father Absent
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Both Parents Absent
\end{minipage} \\
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Any Parent Absent
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Only Mother Absent
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Only Father Absent
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Both Parents Absent
\end{minipage} \\
\midrule
\endhead
Explanator & -0.09** & -0.05 & -0.13* & -0.05 \\
& (0.03) & (0.06) & (0.06) & (0.11) \\
W1 score & -0.61*** & -0.65*** & -0.60*** & -0.63*** \\
& (0.03) & (0.04) & (0.04) & (0.06) \\
Num.Obs. & 1958 & 913 & 897 & 475 \\
R2 & 0.528 & 0.627 & 0.638 & 0.646 \\
R2 Adj. & 0.375 & 0.313 & 0.320 & -0.312 \\
R2 Within & 0.363 & 0.407 & 0.372 & 0.351 \\
FE: clsids & X & X & X & X \\
FE: w2clsids & X & X & X & X \\
\bottomrule
\end{longtable}
